Non-word repetition in Yélî Dnye

### 2020-12-22 manuscript.Rmd
cleaned up and reknitted

knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.pos = "T")
require("papaja")
library(kableExtra)
library(gdata)
library(tidyverse)
library(lme4)

@@

<!-- REMEMBER!!!! -->
<!-- phonetic characters: -->
<!-- - save excel as utf with save as -->
<!-- - do $ iconv -f utf-16le -t utf-8 stimuli.txt > stimconv.txt -->
<!-- - do $ iconv -f utf-16le -t utf-8 segments.txt > segconv.txt -->

## TODO Alex

- check again if all fields are explained
- set up OSF (or revise if already there)
- implement decisions on prop phones & patterns nwr mp
<!--Added by MC on 21 Dec 2020-->
- check and accept/deny MC's updated segment frequencies
- re-run analyses w/ new frequencies and check that outcomes didn't qualitatively change
- check YD data in figure 1 (the effect of item length looks reversed)
- see MC comments throughout and delete now-irrelevant things

## TODO Middy

<!--
- double check my frequency entries in segments.xlsx using the search function in https://phoible.org/parameters; take a look at http://phoible.github.io/conventions/ in case you see something about double articulation (I didn't find tp or lBj)

M2A: Done! Left for AC to review in segments-20201123.xlsx and, if she is satisfied, to integrate :)
-->
<!--
- draft discussion

M2A: Done! I left some space for you to fill in references in a few spots since it seemed from the notes you left that you had some specific ones in mind.
-->

@@

```{r tab2-stims, results = "asis"}
#add orthographic representations targets & other stims chars
stims.tbl <- read_delim("stimuli3.txt", delim = "\t") %>%
  arrange(factor(type, levels = c("practice", "1", "2", "3", "4"))) %>%
  select(type, target_ortho, phono) %>%
  rename("Type" = type, "Orthographic" = target_ortho, "Phonological" = phono)

@@

```{r demo}
# read.csv("NWR-test-log_FINAL.csv",header=T,sep=";")->fulldemo
# fulldemo=fulldemo[,-2] #remove children's names
# fulldemo$dob=as.Date(as.character(fulldemo$DOB.ISO),format="%Y%m%d")
# fulldemo$test=as.Date(as.character(fulldemo$Date),format="%Y%m%d")
# fulldemo$age.rounded=as.numeric(difftime(fulldemo$test,fulldemo$dob,unit="weeks"))/52.25
# fulldemo$Age=as.numeric(as.character(fulldemo$Age))
# plot(fulldemo$Age~fulldemo$age.rounded)
# write.csv(fulldemo,"nwr-demo.csv")

@@

#lines no longer needed
#if family is missing, attribute each child to a different one
#demo$familyID=as.character(demo$familyID)
#demo$familyID[is.na(demo$familyID)]<-paste("k",demo$ID[is.na(demo$familyID)])
#recalc age
#demo$age.rounded=as.numeric(difftime(as.Date(as.character(demo$Date),format="%Y%m%d"),as.Date(as.character(demo$DOB.ISO),format="%Y%m%d"),unit="weeks"))/52.25
#write.table(demo,"nwr-demo.csv",row.names=F,quote=T,sep=",")

@@

```{r Fig2-xling-freq, fig.pos = "!t", fig.align = "center", out.width = '65%', fig.cap="NWR scores for individual target words as a function of the average frequency with which each phone is found across languages."}
aggregate(trnsc.inc$correct*100,by=list(trnsc.inc$target,trnsc.inc$avg_fr),mean)->xling
colnames(xling)<-c("Target","Avg_fr","Word")
stims.ipa <- read_delim("stimuli3.txt", delim = "\t") %>%
  select(target, target_ortho, phono)
xling <- merge(xling, stims.ipa, by.x = "Target", by.y = "target")

>>>>

knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.pos = "T")
require("papaja")
library(kableExtra)
library(gdata)
library(tidyverse)
library(lme4)
library(openxlsx)

@@

@@

```{r tab2-stims, results = "asis"}
#add orthographic representations targets & other stims chars
stims.tbl <- read.xlsx("stimuli.xlsx") %>%
  arrange(factor(type, levels = c("practice", "1", "2", "3", "4"))) %>%
  select(type, target_ortho, phono) %>%
  rename("Type" = type, "Orthographic" = target_ortho, "Phonological" = phono)

@@

```{r demo}
# please note that you will not be able to do this because you don't have this version, that is not fully de-identified
# read.csv("NWR-test-log_FINAL.csv",header=T,sep=";")->fulldemo
# fulldemo=fulldemo[,-2] #remove children's names
# fulldemo$dob=as.Date(as.character(fulldemo$DOB.ISO),format="%Y%m%d")
# fulldemo$test=as.Date(as.character(fulldemo$Date),format="%Y%m%d")
# fulldemo$age.rounded=as.numeric(difftime(fulldemo$test,fulldemo$dob,unit="weeks"))/52.25
# fulldemo$Age=as.numeric(as.character(fulldemo$Age))
# plot(fulldemo$Age~fulldemo$age.rounded)
# write.csv(fulldemo,"nwr-demo.csv")

@@

@@

```{r Fig2-xling-freq, fig.pos = "!t", fig.align = "center", out.width = '65%', fig.cap="NWR scores for individual target words as a function of the average frequency with which each phone is found across languages."}
aggregate(trnsc.inc$correct*100,by=list(trnsc.inc$target,trnsc.inc$avg_fr),mean)->xling
colnames(xling)<-c("Target","Avg_fr","Word")
stims.ipa <- read.xlsx("stimuli.xlsx") %>%
  select(target, target_ortho, phono)
xling <- merge(xling, stims.ipa, by.x = "Target", by.y = "target")
